---
title: "Hello, Penguins!"
author: "Mine Çetinkaya-Rundel"
format: 
  html: default
  pdf: default
editor: visual
execute: 
  echo: true
bibliography: references.bib
---

# Introduction

## Data

For this analysis we'll use the `penguins` dataset from the [**palmerpenguins**](https://allisonhorst.github.io/palmerpenguins/ "Link to palmerpenguins documentation") package.[@gorman2014]

```{r}
#| label: load-packages
#| message: false

library(tidyverse)
library(ggthemes)
library(palmerpenguins)
library(gt)
```

## Species

@fig-bill-dims-species is a bar plot of species of penguins.

```{r}
#| label: fig-bill-dims-species
#| fig-cap: |
#|   A scatterplot of three species of penguins showing the relationship between 
#|   bill depth and bill length.
#| fig-width: 5
#| fig-asp: 0.618
#| fig-alt: |
#|   A scatterplot of three species of penguins showing the relationship between 
#|   bill depth and bill length.
#| warning: false
#| output-location: column-fragment
#| code-line-numbers: "|2|3-6|10"

ggplot(
  penguins,
  aes(
    x = bill_length_mm, y = bill_depth_mm,
    color = species, shape = species
  )
) +
  geom_point() +
  theme_minimal() +
  scale_color_colorblind() +
  labs(x = "Bill length (mm)", y = "Bill depth (mm)")
```

## Penguins

@tbl-penguins-top10 shows the first 10 penguins from the dataset.

```{r}
#| label: tbl-penguins-top10
#| tbl-cap: Top 10 rows of the penguins dataset.

penguins |>
  slice_head(n = 10) |>
  select(species, island, bill_length_mm, bill_depth_mm) |>
  gt()
```

# Analysis

## Model 1 results

::: incremental
-   Some information about the model

-   Some text about results

-   Some comments about shortcomings
:::

## Model 2 results

blah blah blah

## References
